\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usetheme{cern}
\usepackage{wrapfig}

%The CERN logo is legally protected. Please visit http://cern.ch/copyright for information on the terms of use of CERN content, including the CERN logo.

% The optional `\author` command defines the author and is displayed in the slide produced by the `\titlepage` command.
\author{Hannah Short (CERN), Sebastian Lopienski (CERN)}

% The optional `\title` command defines the title and is displayed in the slide produced by the `\titlepage` command.
\title{Evening Session}

% The optional `\subtitle` command will add a smaller title below the main one, and will not be displayed in any of the slides' footer.
\subtitle{CODATA School}

% The optional `\date` command will display a custom free text date on the all of the slides' footer. If omitted today's date will be used.
%\date{Monday, 1st January 2018}

\begin{document}

\frontcover

% The optional `\titlepage` command will create a slide with the presentation's title, subtitle and author.
\frame{\titlepage}

% The optional `\tableofcontents` command will automatically create a table of contents based om the sections.
%\frame{\tableofcontents}

\begin{frame}{This evening}
You have a choice!
\begin{itemize}
\item Crack some encryption ciphers \url{goo.gl/h6Jg5b}
\begin{itemize}
\item You can use anything you like to help (shell script, excel, code...)
\item But... don't use an online decryption site!  
\end{itemize}
\item Participate in group discussions and Q\&A
\end{itemize}
\end{frame}

\begin{frame}{Privacy vs Security}
How much information are you willing to have in the public domain?
\begin{itemize}
\item Would you share airport ``check-ins" on facebook or twitter?
\item Would you share holiday pictures?
\item Would you share your street address?
\item Would you share your genome?
\end{itemize}
\end{frame}

\begin{frame}{How safe is your Smart Watch?}
\begin{itemize}
\item What are possible security problems with Internet of Things devices (IoT)?
\item What are the consequences for Science?
\end{itemize} 
\end{frame}

\begin{frame}{Can you trust your hardware?}
\begin{itemize}
\item Is it possible to trust your laptop?
\end{itemize}
\end{frame}

\begin{frame}{Crypto Challenges}
\url{goo.gl/h6Jg5b}
\end{frame}

\begin{frame}{Crypto Challenge 1 - Caesar Cipher}
Ciphertext: {\small \textit{``pm ol ohk hufaopun jvumpkluaphs av zhf, ol dyval pa pu jpwoly, aoha pz, if zv johunpun aol vykly vm aol slaalyz vm aol hswohila, aoha uva h dvyk jvbsk il thkl vba."} \par} 
Key: ? \newline
Plaintext: ? 
\end{frame}

\begin{frame}{Crypto Challenge 2 - Monoalphabetic Substitution}
Ciphertext: {\small \textit{``dk. afr dkl. rwklstb, gy fwdztk ygwk, hkoxtm rkoxt, ctkt hkgwr mg lab miam mitb ctkt htkytemsb fgkdas, miafq bgw xtkb dwei. mitb ctkt mit salm htghst bgw’r tvhtem mg zt ofxgsxtr of afbmiofu lmkafut gk dblmtkogwl, zteawlt mitb pwlm rorf’m igsr comi lwei fgfltflt."} \par} 
Key: ? \newline
Plaintext: ? 
\end{frame}

\begin{frame}{Crypto Challenge 3 - Vigenere Cipher }
Ciphertext: {\small \textit{``yvhn fr. dwobh bcujigs qt eaz epr dngowbfew tjow hx wqiod lhqfwlr bg qhlxbtowigg jwv eeexsqtr-fkfvt uithkdty ywwh t pcfwy hf udhcban adggihwfegcg, hkeke yov mncj hdld apr hxvivspegt kb koubkhrn."\footnote{Hint: Look around online for information about this Cipher and see if you can use any of the techniques we looked at. Spaces and punctuation are not encrypted in this text, when applying a key of length \(x\) you should exclude them.}} \par}
Key length : 6\newline
Key: ? \newline
Plaintext: ? \newline
\end{frame}

\backcover
\end{document}